The provided datasets contain the following information

An Author dataset with profile information about 250.000 authors, such as author name and affiliation. The same author can appear more than once in this dataset, for instance because he/she publishes under different versions of his/her name, such as T. Heskes or Tom Heskes.

\begin{tabular}{| l | p{8cm} |} \hline
\textbf{Name} & \textbf{Comments} \\ \hline
ID & Id of the author \\ \hline
Name & Author Name \\ \hline
Affiliation & Organization name with which the author is affiliated \\ \hline
\end{tabular}

A Paper dataset with data about 2.5 million papers, such as paper title, conference/journal information, and keywords. The same paper may have been obtained through different data sources and hence have multiple copies in the dataset.

\begin{tabular}{| l | p{8cm} |} \hline
\textbf{Name} & \textbf{Comments} \\ \hline
Id &  Id of the paper \\ \hline
Title & Title of the paper \\ \hline
Year & Year of the paper \\ \hline
ConferenceId & Conference Id in which paper was published \\ \hline
JournalId & Journal Id in which paper was published \\ \hline
Keywords &  Keywords of the paper \\\hline
\end{tabular}

A corresponding Paper-Author dataset with (paper ID, author ID) pairs. The Paper-Author dataset is noisy, containing possibly incorrect paper-author assignments that are due to author name ambiguity and variations of author names.

\begin{tabular}{| l | p{8cm} |} \hline
Name & Comments \\ \hline
PaperId & Paper Id \\ \hline
AuthorId & Author Id \\ \hline
Name  &  Author Name (as written on paper) \\ \hline
Affiliation  & Author Affiliation (as written on paper) \\ \hline
\end{tabular}


Since each paper is either a conference or a journal, additional metadata about conferences and journals is provided where available.

\begin{tabular}{| l | p{8cm} |} \hline
Name & Comments  \\ \hline
Id & Conference Id or Journal Id  \\ \hline
ShortName & Short name  \\ \hline
Fullname & Full name  \\ \hline
Homepage & Homepage URL of conference or journal  \\ \hline
\end{tabular}


Papers that authors have \emph{confirmed} (acknowledging they were the author) or deleted (meaning they were not the author) have been split into Train, Validation, and Test sets based on the author's Id. 

\begin{tabular}{| l | p{8cm} |} \hline
Name & Comments  \\ \hline
AuthorId & Id of the author \\ \hline
DeletedPaperIds & Space-delimited set of deleted papers (Train only)  \\ \hline
ConfirmedPaperIds  & Confirmed papers (Train only)  \\ \hline
PaperIds & PaperIds to rank from most likely to be deleted to least likely (Valid and Test only)  \\ \hline
\end{tabular}