
\section{Co author graph \label{sec:graph-implementation}}

\input{Parts/Implementation-graph.tex}

\section{Text analyses \label{sec:text-implementation}}

\input{Parts/Implementation-text.tex}

\section{Smaller features \label{sec:smaller-features-implementation}}

The data from this also contained smaller, easier to extract, features. The features we also found for \textit{every} paper-author combination.

\begin{itemize}
\item[]Dates. For each author we also include
\begin{itemize}
\item[] First year. The first year the author published a paper. We only looked for papers with a year greater then 1800. All years below are considered bias.
\item[] Last year. The last year the author published a paper. We only looked for papers with a year lower then 2013. All years above are considered bias.
\item[] Average year. Weighted average of all the years the author published a paper.
\item[] Standard deviation of all years
\end{itemize}
\item[] Number of papers written
\item[] Number of journals published in 
\item[] Number of conferences
\end{itemize}


\subsection{Classifying the authors and papers \label{sec:classifier-implementation}}

For our final submission we used two sets of data with the following columns.

\begin{itemize}
\item [] AuthorID 
\item [] PaperID 
\item [] $score_1 \cdots \cdots score_{20}$ 
\item [] First year 
\item [] Last year 
\item [] Average year 
\item [] Average group size
\item [] Number of authors in paper
\item [] Year Standard deviation 
\item [] Number of papers written
\item [] Number of journals published in 
\item [] Number of conferences
\end{itemize}

We only used the valid set to train our classifier. After we trained the classifier we applied the classifier to the test set. because the classifier also gives a probability we used that to rank the outcome.




