\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{float}

\title{KDD Cup 2013 - Author-Paper Identification Challenge}
\author{ Mike Koeman \and Vincent Slieker   \and Aram Verstegen \and Rob Tiemens}
\graphicspath{./Images/} 

\begin{document}

\maketitle


\begin{abstract}
The ability to search literature and collect and aggregate metrics around publications is a central tool for modern research. Both academic and industry researchers across hundreds of scientific disciplines, from astronomy to zoology, increasingly rely on search to understand what has been published and by whom.

The profile of an author with an ambiguous name tends to contain noise, resulting in papers that are incorrectly ascribed to them. This KDD Cup task challenges participants to determine which papers in an author profile were truly written by a given author.

We researched and adapted two novel methods to cope with these problems. We used a text analysis method to collect research topics, these topics are then treated as new features to classify paper-author combinations. An advanced graph database was used to create a social network graph from all authors. Examining the relations between authors should reveal useful information to place a writer in a social context, from which we can extract features relating to their closeness.
\end{abstract}

\nocite{chowdhury2010introduction}
\nocite{liu2005co}
\nocite{glanzel2005analysing}
\nocite{morel2009co}
\nocite{niels2008writer}
\nocite{steyvers2004probabilistic}
\nocite{newman2004coauthorship}
\nocite{Liu:2006:WDM:1215470}
\nocite{Witten:2005:DMP:1205860}


\input{Parts/Introduction.tex}

\input{Parts/Background.tex}

\input{Parts/Implementation.tex}

\input{Parts/Results.tex}

\input{Parts/Conclusion.tex}

\appendix
\section{Appendix: Data  \label{sec:data-background}}
\input{Parts/Background-data.tex}

\bibliographystyle{alpha}
\bibliography{references}


\end{document}
